% Section: Introduction — P8 commit 2.
% Numerical claims verified against:
%   - results/p7_8_solver_h1_n24/h1_analysis_combined_n24.json
%   - results/p5_h1_verdict/h1_analysis.json
%   - results/p7_8_kdv_gate/gate_result.json
%   - ODE_PDE_PRE_REG.md (pre-registration)
%   - PRE_REG_AMENDMENT.md (A1--A11)
% All non-numerical claims are cited from refs in paper/references.bib.

\section{Introduction}
\label{sec:intro}

The question of whether variational quantum machine-learning (QML)
models offer a useful advantage over classical neural networks
remains contested~\cite{schuld2019quantum,havlicek2019supervised,
caro2022generalization}. Schuld and Killoran observed that the field
should pursue \emph{regime-dependent} advantages rather than blanket
quantum supremacy claims~\cite{schuld2022right}: a quantum model is
``useful'' if it solves a specific class of problems better than the
best matched classical model at the same parameter budget.
Physics-informed neural networks (PINNs) — the mesh-free continuous
trial solutions introduced by Raissi, Perdikaris, and
Karniadakis~\cite{raissi2019physics} and surveyed
in~\cite{karniadakis2021physics,lu2021deepxde} — provide a natural
substrate to ask this question, because the differential-equation
residual loss is a single scalar that depends on the model class
through a clean derivative-of-parameterized-function interface and
admits matched classical baselines~\cite{wang2022whenwhy} and
operator-learning competitors~\cite{lu2021deeponet,li2021fourier}.
The landscape of \emph{quantum physics-informed neural networks}
(quantum PINNs)~\cite{perezsalinas2020dataru,kyriienko2021solving,
markidis2022physics,berger2025teqpinn,sedykh2024quantum,
farea2025qcpinn,ahmed2024rfqrc} has produced several candidate
ansätze with theoretically motivated regime-dependence claims, most
prominently the prediction that the
data-reuploading Fourier series accessible to a quantum
circuit~\cite{schuld2021effect} grants an
inductive bias for smooth, periodic dynamics. Yet the empirical
picture is fragmentary: most quantum-PINN papers report a single
task, often without matched classical baselines or pre-registered
acceptance criteria, leaving the central question \textit{when, and
on what kinds of problems, does a quantum PINN outperform a
capacity-matched classical PINN?} unanswered at any rigorous level.

Bowles, Ahmed, and Schuld recently catalogued the methodological
gaps that make existing QML benchmarks
unreliable~\cite{bowles2024better,huang2025qml}: tuning the
classical baseline insufficiently, comparing at mismatched parameter
counts, reporting only the best-of-many random seeds, and citing
isolated wins rather than statistically defensible
contrasts. They propose a set of
methodological commitments \textemdash{} pre-registration, matched
training budgets, paired bootstrap confidence intervals, an
underfit guard, and a known-structure ``skyline'' baseline
\textemdash{} that any quantum advantage claim should satisfy. To
our knowledge no published quantum-PINN benchmark has yet
implemented this complete framework on a hardness ladder spanning
both ordinary and partial differential equations.

\paragraph{Methodological lineage.}
The framework this paper implements sits at the intersection of three
methodological lineages. From the classical PINN
literature~\cite{raissi2019physics,karniadakis2021physics,
lu2021deepxde} we inherit the mesh-free continuous trial-solution
formulation and the physics-residual loss closure, including the
known training-pathology
caveats~\cite{krishnapriyan2021characterizing,wang2022whenwhy}
that constrain matched-capacity comparison. From the variational
QML literature~\cite{schuld2019quantum,havlicek2019supervised,
schuld2021effect,caro2022generalization} we inherit the
data-reuploading ansatz family, the Fourier-series expressivity
analysis, and the Meyer--Wallach $Q$ /
KL-to-Haar~\cite{holmes2022connecting} trainability scalars used in
the H3 mechanism cross-tabulation. From the QML-benchmarking
literature~\cite{bowles2024better,huang2025qml} we inherit the
methodological commitments enumerated above
\textemdash{} pre-registration, matched training budgets, paired
bootstrap, underfit + skyline guards, and symmetric HPO sensitivity.
The synthesis these three lineages enable, applied to a
pre-registered ODE+PDE hardness ladder with a mechanically gated
reproducibility script and twenty-two openly-documented
amendments, is the methodological contribution of this work, even
when (as in our case) the empirical hypothesis it tests is
falsified.

This work executes exactly such a benchmark. Following a
pre-registration committed before any results were generated
(Appendix~A; Methods~\ref{sec:methods}), we test the hypothesis
that quantum PINNs achieve a regime-dependent advantage in
smooth/periodic versus broadband/multiscale dynamical systems.
Four quantum-PINN families
\textemdash{} the data-reuploading universal classifier
ansatz~\cite{perezsalinas2020dataru}, the
trainable-embedding QPINN with classical FNN encoder and with QNN
encoder variants~\cite{berger2025teqpinn}, and the quantum-classical
hybrid QCPINN~\cite{farea2025qcpinn} \textemdash{} are run against
capacity-matched classical PINN and non-liquid Neural-ODE
baselines on four ODEs (\lv{}, \vdp{}, Lorenz, \fhn{}) and
four PDEs (heat, smooth Burgers, \ac{}, shock Burgers), at three
random seeds each (24 cells total). The
hardness ladder is pre-registered with explicit regime tags:
smooth/periodic for \lv{}, \vdp{}, heat, and smooth Burgers;
broadband/multiscale for Lorenz, \fhn{}, \ac{}, and shock
Burgers.

The pre-registered hypothesis is FALSIFIED. The combined
solver-task verdict at $n=24$ is
$\ddiff = \dsmooth - \dbroad = -0.084$ with paired-bootstrap 95\%
confidence interval $[-0.278, +0.061]$. Four additional layered
sensitivity points \textemdash{} the forecaster-task verdict at
$n=9$ ($\ddiff = -0.42$, CI excludes zero in the
\emph{negative} direction~\cite{schuld2022right}), the
default-Adam combined verdict at the pre-expansion
$n=18$ ($\ddiff = +0.032$, CI $[-0.040, +0.109]$), the
both-sides hyperparameter-optimized verdict at $n=9$
($\ddiff = +0.059$, CI $[-0.058, +0.191]$), and the $n=24$
verdict reported above \textemdash{} all return the same
qualitative result: no statistically distinguishable regime-dependent
advantage at this matched-capacity, matched-budget compute.
Notably, the point estimate flips sign as the broadband bin is
expanded from six to twelve cells, suggesting (without
statistical significance) the \emph{inverse} of the original
hypothesis: a tendency toward broad-over-smooth quantum
advantage. We treat this consistency-across-sensitivity-points as
the paper's principal scientific finding: at the matched-capacity
scale, on this pre-registered ladder, the regime-dependent
quantum-PINN advantage hypothesis does not survive.

Within the falsification, the expanded ladder surfaces a positive
sub-finding worth reporting on its own terms. The trainable-embedding
quantum PINN with QNN encoder
(\texttt{te\_qpinn\_qnn})~\cite{berger2025teqpinn}
achieves a structural advantage on \fhn{} that was invisible at
$n=18$: across three seeds it attains
$\relltwo = 0.327, 0.356, 0.329$ \textemdash{} a seed-variance
twenty-four times tighter than the matched classical PINN
(0.640, 0.641, 1.326; one cell exhibits a catastrophic training
failure). The seed-mean advantage is roughly twofold (0.337
versus 0.870). This is a clear regime-specific structural QLNN
edge on stiff fast--slow dynamics, observed at zero classical
parameters in the ansatz and at the same training budget as
every other cell.

This paper makes four contributions.
\begin{enumerate}
\item \textbf{Methodological.} An open-source benchmarking
  framework for quantum PINN comparison that implements all of
  Bowles, Ahmed, and Schuld's recommendations~\cite{bowles2024better}:
  pre-registration with falsifiable acceptance rules, matched
  parameter budgets, paired-bootstrap inference, an underfit
  guard, a known-structure skyline guard, symmetric
  hyperparameter sensitivity (both quantum and classical sides
  tuned at three learning rates and two training-step budgets at
  three anchor cells), and a \texttt{verify\_paper\_integrity}
  script that mechanically checks every cited number in the
  paper against a committed JSON file. Eleven pre-registration
  amendments are documented openly (Appendix~A).
\item \textbf{Empirical.} A pre-registered regime-dependent
  advantage hypothesis is FALSIFIED at five layered sensitivity
  points covering eight of the nine pre-registered hardness-ladder
  systems and both pre-registered tasks (solver and forecaster).
  A positive structural sub-finding (\texttt{te\_qpinn\_qnn} on
  \fhn{}) is identified at the same compute budget.
\item \textbf{Mechanistic.} The H3 cross-tabulation links the
  per-cell advantage gap to trainability and expressivity
  scalars (Kullback--Leibler divergence to a Haar-random unitary
  ensemble, Fourier $K_{\max}$ accessible to the
  ansatz~\cite{schuld2021effect}, gradient variance, and barren
  plateau scaling). The KL-to-Haar trend
  ($\rho_{\mathrm{Spearman}} = +0.518$) is statistically
  underpowered at $n=9$ but leave-one-out robust (all nine
  resamples give the same sign), and consistent with the
  inverted-pattern reading.
\item \textbf{Open-source artifact.} The full code, data, and
  reproduction pipeline are released at
  \url{https://github.com/shawngibford/qlnn}, including
  \texttt{scripts/reproduce\_paper.sh} (regenerates every result),
  \texttt{scripts/verify\_paper\_integrity.py} (gates the cited
  numbers), and tagged GitHub releases at the post-rigor and
  post-airtight-matrix checkpoints. The reproducibility commitments
  follow the NeurIPS 2019 program guidance~\cite{pineau2021improving}
  on environment pinning, seed determinism, and post-hoc auditability
  of cited numbers.
\end{enumerate}

\subsection*{What this paper does \emph{not} claim}

To be precise about scope: this paper does not claim a quantum
advantage; it claims its \emph{absence} at this matched-capacity,
matched-budget scale. It does not claim that the H1 hypothesis is
false in general — only that the pre-registered acceptance
threshold is not crossed on this hardness ladder. It does not
claim that the broadband-leaning point estimate sign is reliable;
the confidence interval crosses zero on every sensitivity point and
no multiple-comparison correction~\cite{benjamini1995controlling,
demsar2006statistical} is invoked because the headline verdict is
not significance-positive in either direction. It does not assert
generalization from $n=24$ cells to the full QML/PDE landscape;
the cited follow-up papers (Section~\ref{sec:discussion}) are
precisely the experiments needed to address that gap.

Two extensions were proven feasible by mechanism gates but
deferred for compute budget reasons. The triple-nested
reverse-mode autodiff through a PennyLane QNode required to solve
the KdV equation ($u_t + 6 u u_x + u_{xxx} = 0$) is
shown to produce finite, non-trivial values at the canonical
Chebyshev-DQC 2D circuit shape, at $\approx 0.44\times$ the
per-point cost of the second-order autodiff that underlies the
heat, Burgers, and Allen--Cahn solvers (Methods,
Section~\ref{sec:methods}). The integrated training cost across
3 seeds, 4 quantum families, and the classical-PINN baseline
remains prohibitive at our budget; the gate-passed mechanism is
queued for a follow-up paper. Similarly, the 12-dimensional
Kuramoto system from the pre-registration is mechanically
supported by our per-component scalar circuits but is twelve times
the compute of the 2D ODEs in our matrix; it is queued for the
same follow-up.

The rest of the paper proceeds as follows. Methods
(Section~\ref{sec:methods}) details the pre-registration, the
quantum-PINN family roster, the matched baselines, and the
verdict machinery. Solver-task results
(Section~\ref{sec:solver}) report the per-cell error tables
and the four falsification points on the solver task.
Forecaster-task results (Section~\ref{sec:forecaster}) report
the corroborating verdict on the data-driven track. The H1
verdict and sensitivity analysis (Section~\ref{sec:verdict})
aggregates the five sensitivity points and discusses the
sign-flip behavior under sample-size expansion. The mechanism
(Section~\ref{sec:mechanism}) cross-tabulates the per-cell gap
with trainability scalars. Discussion
(Section~\ref{sec:discussion}) covers limitations and future
work. Conclusions (Section~\ref{sec:conclusions}) summarizes
what the negative result and the positive sub-finding mean for
the quantum-PINN program going forward.
