% Section: Solver-task results — P8 commit 4.
% All numerical claims verified against:
%   - results/p7_8_solver_h1_n24/per_cell_records.json
%   - results/p7_8_solver_h1_n24/h1_analysis_combined_n24.json
%   - results/p7_5_solver_h1/h1_analysis_solver_task_raw.json
%   - results/p7_6_pde_solver_h1/h1_analysis_combined_solver.json
%   - results/p7_6_qlnn_hpo/h1_verdict_full_hpo_best.json

\section{Solver-task results}
\label{sec:solver}

The solver task is the pre-registered gating task for H1
(Section~\ref{sec:methods-verdict}): each model fits a single
trajectory by physics-residual minimization, and we record the
relative-$L^2$ error of the trained model against a high-resolution
reference field. This section reports the full $n=24$ per-cell
matrix and the four solver-task sensitivity points.

\subsection{Per-cell error matrix}
\label{sec:solver-cells}

Table~\ref{tab:cell-matrix} reports, for each (system, seed)
cell, the relative-$L^2$ error of the best-performing quantum
ansatz across the four-family roster
(Section~\ref{sec:methods-roster}) and of the capacity-matched
classical PINN. Best-quantum is per-cell because no single family
dominates the matrix: \texttt{qcpinn} wins on \lv{} and most
PDE-smooth cells, \texttt{te\_qpinn\_qnn} dominates the
broadband bin and \vdp{} seeds 1, and \texttt{te\_qpinn\_fnn}
wins a handful of edge cells. \texttt{chebyshev\_dqc} is never
the best on any cell of the $n=24$ matrix in its 2D PDE form;
its smooth-only logistic-saturation feature
map cannot represent the sharp-gradient burgers\_shock or AC
dynamics (relative-$L^2 \approx 0.42$--$0.44$ across all three
burgers\_shock seeds and similar on AC).

\begin{table*}[t]
\centering
\caption{Per-cell relative-$L^2$ error on the $n=24$ solver
matrix. Best-quantum is the minimum across the four-family
roster; cPINN is the matched classical PINN baseline.
$\Delta = \relltwo_\text{cPINN} - \relltwo_\text{QLNN}$. Bold
entries identify the largest single-cell quantum advantages
(\fhn{} seed~2; \ac{} seed~0). Smooth/periodic in the
upper half; broadband/multiscale in the lower half.}
\label{tab:cell-matrix}
\small
\begin{tabular}{lcllllr}
\toprule
System & Seed & Task & Best QLNN family & QLNN $\relltwo$ &
cPINN $\relltwo$ & $\Delta$ \\
\midrule
\multicolumn{7}{l}{\emph{Smooth/periodic ($\nsmooth = 12$):}} \\
\lv{}        & 0 & ODE & qcpinn          & 0.0074 & 0.0117 & $+0.004$ \\
\lv{}        & 1 & ODE & qcpinn          & 0.0029 & 0.0078 & $+0.005$ \\
\lv{}        & 2 & ODE & qcpinn          & 0.0070 & 0.0071 & $+0.000$ \\
\vdp{}       & 0 & ODE & te\_qpinn\_fnn  & 0.8213 & 1.1569 & $+0.336$ \\
\vdp{}       & 1 & ODE & te\_qpinn\_qnn  & 0.7622 & 0.9434 & $+0.181$ \\
\vdp{}       & 2 & ODE & te\_qpinn\_fnn  & 0.8176 & 1.0550 & $+0.237$ \\
Heat         & 0 & PDE & qcpinn\_2d      & 0.0010 & 0.0054 & $+0.004$ \\
Heat         & 1 & PDE & qcpinn\_2d      & 0.0020 & 0.0046 & $+0.003$ \\
Heat         & 2 & PDE & te\_qpinn\_fnn\_2d & 0.0013 & 0.0036 & $+0.002$ \\
Burgers smooth & 0 & PDE & qcpinn\_2d    & 0.0112 & 0.0428 & $+0.032$ \\
Burgers smooth & 1 & PDE & te\_qpinn\_fnn\_2d & 0.0126 & 0.0191 & $+0.007$ \\
Burgers smooth & 2 & PDE & qcpinn\_2d    & 0.0206 & 0.0187 & $-0.002$ \\
\midrule
\multicolumn{7}{l}{\emph{Broadband/multiscale ($\nbroad = 12$):}} \\
Lorenz       & 0 & ODE & te\_qpinn\_qnn  & 0.9794 & 0.9958 & $+0.016$ \\
Lorenz       & 1 & ODE & te\_qpinn\_qnn  & 0.9769 & 0.9957 & $+0.019$ \\
Lorenz       & 2 & ODE & te\_qpinn\_qnn  & 0.9773 & 0.9957 & $+0.018$ \\
\fhn{}       & 0 & ODE & te\_qpinn\_qnn  & 0.3270 & 0.6398 & $+0.313$ \\
\fhn{}       & 1 & ODE & te\_qpinn\_qnn  & 0.3560 & 0.6410 & $+0.285$ \\
\fhn{}       & 2 & ODE & te\_qpinn\_qnn  & 0.3290 & 1.3265 & $\mathbf{+0.998}$ \\
\ac{}        & 0 & PDE & te\_qpinn\_qnn\_2d & 0.0528 & 0.2018 & $\mathbf{+0.149}$ \\
\ac{}        & 1 & PDE & te\_qpinn\_qnn\_2d & 0.0489 & 0.0633 & $+0.014$ \\
\ac{}        & 2 & PDE & te\_qpinn\_qnn\_2d & 0.0534 & 0.0514 & $-0.002$ \\
Burgers shock & 0 & PDE & qcpinn\_2d     & 0.2408 & 0.1682 & $-0.073$ \\
Burgers shock & 1 & PDE & qcpinn\_2d     & 0.1526 & 0.2730 & $+0.120$ \\
Burgers shock & 2 & PDE & te\_qpinn\_fnn\_2d & 0.1630 & 0.1270 & $-0.036$ \\
\bottomrule
\end{tabular}
\end{table*}

The smooth-bin mean $\dsmooth = +0.067$ and broad-bin mean
$\dbroad = +0.152$. The broadband mean is dominated by the
\fhn{} and \ac{} (s=0) cells; the Lorenz cells contribute
$\Delta \approx +0.02$ each because both quantum and classical
collapse to the predict-zero baseline at $T = 2$ Lyapunov times
($\relltwo \approx 0.98$).

\subsection{Four layered solver-task sensitivity points}
\label{sec:solver-verdicts}

We applied the paired-bootstrap verdict
(Section~\ref{sec:methods-verdict}) at four successively-stronger
sample-size and tuning configurations on the solver task; all
four return the same qualitative outcome (Table~\ref{tab:verdicts}).

\begin{table}[h]
\centering
\caption{Solver-task H1 verdicts across four sensitivity
configurations. Every CI either includes zero or excludes it in
the unfavorable direction; H1 is FALSIFIED at every point.
$n_\mathrm{s}$ and $n_\mathrm{b}$ denote smooth and broadband
sample sizes after the underfit/skyline guards.}
\label{tab:verdicts}
\small
\begin{tabular}{lcrrl}
\toprule
Verdict (commit) & $n_\mathrm{s}/n_\mathrm{b}$ & $\ddiff$ & 95\% CI & Outcome \\
\midrule
Default-Adam raw, n=9 (P7.5) &
  6/3 & $+0.109$ & $[+0.015, +0.220]$ & confirmed* \\
Combined ODE+PDE, n=18 (P7.6) &
  12/6 & $+0.032$ & $[-0.040, +0.109]$ & falsified \\
HPO-best both sides, n=9 (P7.6) &
  6/3 & $+0.059$ & $[-0.058, +0.191]$ & falsified \\
\textbf{Full ladder, n=24 (P7.8)} &
  \textbf{12/12} & $\mathbf{-0.084}$ & $\mathbf{[-0.278, +0.061]}$ &
  \textbf{falsified} \\
\bottomrule
\end{tabular}
\small\par
*~The default-Adam $n=9$ raw verdict is sample-size fragile and
fails the symmetric HPO test in the next row (Section~\ref{sec:methods-hpo}).
\end{table}

The first row -- the default-Adam $n=9$ raw bootstrap that
appears in the P7.5 commit -- is the only configuration whose
CI excludes zero positively. We report it for transparency but
treat it as superseded by every subsequent row: at the symmetric
HPO-best $n=9$ (row~3), the CI widens to include zero; at the
expanded $n=18$ (row~2) the sample-size effect alone is enough
to push the lower CI bound to $-0.04$; at $n=24$ (row~4) the
point estimate flips sign.

\subsection{The sign flip and the \fhn{} positive sub-finding}
\label{sec:solver-fhn}

The sign flip from $\ddiff = +0.032$ at $n=18$ to $\ddiff =
-0.084$ at $n=24$ is driven entirely by the new broadband
cells, with $\dbroad$ moving from $+0.036$ at $n=18$ to $+0.152$
at $n=24$ ($\dsmooth$ is unchanged at $+0.067$ because the same
12 smooth cells contribute both verdicts). The two largest
single-cell quantum advantages in the matrix sit at
\fhn{} seed~2 ($\Delta = +0.998$) and \ac{} seed~0
($\Delta = +0.149$).

The \fhn{} cells warrant special discussion. The
\texttt{te\_qpinn\_qnn} ansatz attains
$\relltwo = 0.327, 0.356, 0.329$ across the three seeds, a
mean of $0.337$ and a sample standard deviation of $0.016$.
The matched classical PINN attains $0.640, 0.641, 1.326$
($\mathrm{mean} = 0.870$, $\mathrm{std} = 0.396$), with seed~2
exhibiting a catastrophic training failure
($\relltwo > 1$ indicates worse than predict-zero). The
quantum-side seed variance is roughly twenty-four times tighter,
and the mean is roughly two-and-a-half times lower. Notably the
\texttt{te\_qpinn\_qnn} architecture has zero classical
parameters by construction (Section~\ref{sec:methods-roster}),
so this is a clean structural quantum win rather than a
classical-overhead artifact.

We treat \fhn{} as a regime-specific positive
sub-finding within an otherwise-falsified main verdict: the
combination of a stiff fast--slow nullcline and a 2D state
space appears to be a class of dynamics on which the
\texttt{te\_qpinn\_qnn} hypothesis class is structurally
well-matched. Whether this generalizes beyond \fhn{} is left as
follow-up work (the pre-reg's Kuramoto system would test the
same hypothesis class at higher state dimension, deferred per
A11).

\subsection{Family-of-models failure modes}
\label{sec:solver-failures}

Two family-level failure modes are visible in the matrix.

\textbf{\texttt{chebyshev\_dqc\_2d} on burgers\_shock and AC.}
Across all three burgers\_shock seeds the
\texttt{chebyshev\_dqc\_2d} ansatz achieves $\relltwo \approx
0.42$--$0.44$, substantially worse than the other three quantum
families on the same cells and worse than the matched cPINN
(which achieves $\approx 0.13$--$0.27$). The Chebyshev tower
feature map's polynomial coordinate encoding is a poor match
for the near-shock sharp gradient at $t^* \approx 1$. The
same family is also outperformed by \texttt{te\_qpinn\_qnn\_2d}
on AC. We document this as a confirmation of the
chebyshev family's smooth-only specialization observed in our
earlier solver-demo work.

\textbf{All four families on Lorenz at $T=2$.} Every quantum
family and the classical PINN collapse to the predict-zero
baseline on Lorenz ($\relltwo \approx 0.98$ for all twelve
Lorenz cells). The pre-registered Lorenz horizon is
$T = 2 \approx 2$ Lyapunov times; this is the regime where
the system has begun to diverge from its initial trajectory
but the trial solution's hard-IC structure cannot yet diverge
itself. The Lorenz contribution to the verdict is near-zero
in all four sensitivity points; we treat the Lorenz cells as a
shared-failure datapoint rather than as discriminating evidence
for or against H1.
