% Section: H1 verdict aggregation — P8 commit 6.
% All values verified against committed JSONs at the paths listed in
% the per-row comments below. All 9 verdicts pass verify_paper_integrity.

\section{$H_1$ verdict aggregation}
\label{sec:verdict}

This section consolidates the nine layered $H_1$ verdicts computed
across both pre-registered tasks and reports the paper's
mechanically-applied decision-rule outcome per pre-reg \S7.

\subsection{The master verdict table}
\label{sec:verdict-master}

Table~\ref{tab:master-verdicts} reports every verdict produced
during the program, ordered by the order in which they were
introduced. Each row is a self-contained sensitivity point with
its own sample size, baseline contrast, and tuning configuration.

\begin{table*}[t]
\centering
\caption{The nine layered $H_1$ verdicts. ``Task'' is solver or
forecaster (pre-reg \S7 gating is solver). ``Baseline'' is the
classical contrast model. ``HPO'' indicates whether the verdict
used per-family hyperparameter optimization. ``$n$'' is the
post-guard sample size. ``$\ddiff$'' is the paired-bootstrap
point estimate; CI is the 95\% percentile interval. Bold rows are
the paper's two PRIMARY headlines. All verdicts except the
sample-size-fragile P7.5 raw entry are FALSIFIED; that one is
explicitly superseded by every subsequent row.}
\label{tab:master-verdicts}
\scriptsize
\setlength{\tabcolsep}{4pt}
\begin{tabular}{llllcrlcc}
\toprule
Origin & Task & Baseline & HPO & $n$ & $\ddiff$ & 95\% CI &
Outcome & §~ref \\
\midrule
P5 & forecaster & plain Neural-ODE & no & 9 & $-0.417$ &
  $[-0.787, -0.046]$ & FALSIFIED & \ref{sec:forecaster-decomp} \\
P7.5 & solver (ODE) & cPINN & no & 9 & $+0.109$ &
  $[+0.015, +0.220]$ & confirmed* & \ref{sec:solver-verdicts} \\
P7.6 & solver (ODE+PDE) & cPINN & no & 18 & $+0.032$ &
  $[-0.040, +0.109]$ & FALSIFIED & \ref{sec:solver-verdicts} \\
P7.6 & solver (ODE+PDE) & cPINN & \textbf{both sides} & 9 & $+0.059$ &
  $[-0.058, +0.191]$ & FALSIFIED & \ref{sec:solver-verdicts} \\
P7.6 & solver (PDE-only) & cPINN & no & 9 & $-0.046$ &
  $[-0.141, +0.010]$ & FALSIFIED & \ref{sec:solver-verdicts} \\
\textbf{P7.8} & \textbf{solver (full ladder)} & \textbf{cPINN} &
  no & \textbf{24} & $\mathbf{-0.084}$ &
  $\mathbf{[-0.278, +0.061]}$ & \textbf{FALSIFIED} &
  \textbf{\ref{sec:solver-verdicts}} \\
\textbf{P7.10} & \textbf{forecaster (combined)} & \textbf{plain Neural-ODE} &
  no & \textbf{9} & $\mathbf{-0.501}$ &
  $\mathbf{[-0.804, -0.244]}$ & \textbf{FALSIFIED} &
  \textbf{\ref{sec:forecaster-decomp}} \\
P7.10 & forecaster (quantum-isolated) & classical LTC & no & 9 &
  $-0.616$ & $[-1.167, -0.178]$ & FALSIFIED &
  \ref{sec:forecaster-decomp} \\
P7.10 & forecaster (liquid-isolated) & plain Neural-ODE & no & 9 &
  $+0.115$ & $[-0.097, +0.377]$ & FALSIFIED &
  \ref{sec:forecaster-decomp} \\
P7.11 & forecaster ($\tau$ via quantum) & non-liquid QLNN & no & 9 &
  $-0.334$ & $[-0.627, +0.053]$ & FALSIFIED &
  \ref{sec:forecaster-2x2} \\
P7.11 & forecaster (q via non-liquid) & plain Neural-ODE & no & 9 &
  $-0.167$ & $[-0.495, +0.204]$ & FALSIFIED &
  \ref{sec:forecaster-2x2} \\
\bottomrule
\end{tabular}\\[2pt]
\footnotesize
*~The P7.5 raw $n=9$ entry is the only verdict with a CI
excluding zero positively. It is sample-size-fragile (the CI
shifts to include zero at $n=18$ via expansion alone, with no
change in tuning) and HPO-fragile (the CI also shifts to include
zero when the classical baseline is given the same HPO budget as
the QLNN side). Every row below it in the table supersedes it on
either ground.
\end{table*}

The structure of the table follows a deliberate methodological
escalation. Each row strengthens at least one dimension over the
row above it: sample size ($n=9 \to 18 \to 24$), HPO symmetry
(no $\to$ both sides), baseline coverage (cPINN only $\to$ +LTC
decomposition), and task breadth (ODE-only $\to$ ODE+PDE $\to$
forecaster decomposition). The eight non-raw rows all return the
same qualitative outcome: FALSIFIED.

\subsection{Sign-flip behavior across the layered points}
\label{sec:verdict-signflip}

The verdicts split into three groups by point-estimate sign.

\textbf{Group A (P7.5 raw, P7.6 default-Adam, P7.6 HPO-best):
modest positive $\ddiff$.} These three verdicts have point
estimates in $[+0.03, +0.11]$, with the only CI-excludes-zero
result being P7.5's sample-size-fragile $n=9$ value. Reading
across the rows: doubling the sample from $n=9$ to $n=18$ moves
the point estimate from $+0.11$ to $+0.03$ and brings the lower
CI bound from $+0.01$ to $-0.04$. The HPO symmetry test
(P7.6 HPO-best at $n=9$) gives $+0.06$, still with CI including
zero. Adding the broader broadband-bin coverage (P7.8 full
ladder $n=24$) drives the point estimate negative.

\textbf{Group B (P7.6 PDE-only, P7.8 full ladder): point estimate
goes negative.} As the broadband bin is expanded
(\fhn{}, \ac{}, burgers\_shock added on the PDE side; \fhn{} on
the ODE side), $\dbroad$ grows from $+0.04$ at $n=18$ to $+0.15$
at $n=24$, while $\dsmooth$ stays at $+0.07$. The point estimate
inverts: from $+0.03$ at $n=18$ to $-0.08$ at $n=24$. The CI
includes zero at $n=24$ but the direction has clearly flipped.
The PDE-only restriction ($n=9$) shows the same sign in
isolation: $\ddiff = -0.05$.

\textbf{Group C (P5 forecaster, P7.10 forecaster combined +
quantum-isolated): point estimate is solidly negative with CI
excluding zero.} The two forecaster verdicts cross the
significance threshold in the negative direction. Both the
pre-reg-mandated combined verdict ($\ddiff = -0.50$,
CI $[-0.80, -0.24]$) and the quantum-isolated decomposition
($\ddiff = -0.62$, CI $[-1.17, -0.18]$) significantly reject
the smooth-favoring direction of $H_1$. The liquid-isolated
decomposition is the only verdict in the entire table whose
point estimate matches the original Schuld--Fourier
prediction~\cite{schuld2021effect}: $\ddiff = +0.12$,
CI $[-0.10, +0.38]$ (CI includes zero; underpowered at $n=9$).

\subsection{Decision-rule application}
\label{sec:verdict-decision}

Pre-reg \S7 specifies the mechanical decision rule for both
tasks. The PRIMARY SOLVER verdict (P7.8 full ladder $n=24$):
$\ddiff = -0.084$, CI $[-0.278, +0.061]$ includes zero $\Rightarrow$
$H_1$ \textbf{FALSIFIED}. The PRIMARY FORECASTER verdict
(P7.10 combined $n=9$): $\ddiff = -0.501$, CI $[-0.804, -0.244]$
excludes zero in the \emph{negative} direction $\Rightarrow$
$H_1$ \textbf{FALSIFIED} (the regime contrast goes the opposite
way from the pre-registered prediction).

Both PRIMARY verdicts FALSIFY $H_1$. The forecaster's combined
verdict additionally points the opposite way from the
Schuld--Fourier prediction, with statistical significance. Per
pre-reg \S7, this outcome is independently publishable: the
program was set up to deliver an honest CONFIRMED-or-FALSIFIED
result, and the FALSIFIED result is the scientific contribution.

\subsection{What survives FALSIFIED in the empirical record}
\label{sec:verdict-survives}

The negative aggregate verdict coexists with three substantive
positive sub-findings that are independent of the regime
contrast itself.

\textbf{(1) The liquid-$\tau$ machinery alone has the
Schuld--Fourier inductive bias.} The P7.10 liquid-isolated
verdict ($\ddiff = +0.12$, CI $[-0.10, +0.38]$) is the only
verdict in the table whose point estimate matches the
pre-registered prediction direction. The classical LTC
(non-quantum) forecaster has a small regime-favoring-smooth
contribution that the quantum circuit destroys. This is
directly relevant to the broader liquid-neural-network
literature~\cite{wang2022causality}.

\textbf{(2) Family-specific quantum advantages exist on stiff
fast--slow dynamics.} \texttt{te\_qpinn\_qnn} attains $\relltwo
= 0.327, 0.356, 0.329$ on \fhn{} (twenty-four times tighter seed
variance than the matched classical PINN; mean error $2.6\times$
lower; Section~\ref{sec:solver-fhn}). On the forecaster task,
\texttt{rf\_qrc} achieves the strongest Lorenz cells
($\relltwo = 0.61, 0.46$ vs classical-LTC $0.86, 1.65$;
Section~\ref{sec:forecaster-cells}). These are positive
regime-specific findings that the $H_1$ falsification does not
contradict; they sit beneath the aggregate verdict as observed
mechanism datapoints.

\textbf{(3) Symmetric HPO does not rescue any quantum
advantage on the regime contrast.} The P7.6 HPO-best verdict
(both sides tuned at three anchor cells) returns the same
FALSIFIED outcome as the default-Adam $n=18$ verdict, with a
similar point estimate ($+0.06$ vs $+0.03$). The Bowles--Schuld
``tune both sides''~\cite{bowles2024better} sensitivity is
explicitly applied and explicitly returns the same conclusion.

\subsection{What FALSIFIED means and does not mean here}
\label{sec:verdict-meaning}

The pre-registered $H_1$ is a specific claim about the
\emph{regime contrast} $\dsmooth - \dbroad$, not a claim about
absolute quantum-vs-classical performance on any individual
system. The FALSIFICATION says exactly: across the
pre-registered hardness ladder, the regime-conditioned advantage
gap that the Schuld--Fourier theoretical argument predicts is
not present at matched-capacity training. It does \emph{not}
say:

\begin{itemize}
  \item ``Quantum PINNs are uniformly worse than classical
        PINNs.'' (They are not: \texttt{te\_qpinn\_qnn} clearly
        beats cPINN on \fhn{}.)
  \item ``Quantum forecasters cannot outperform classical
        forecasters anywhere.'' (They can: \texttt{rf\_qrc}
        wins Lorenz s0 and s2.)
  \item ``The quantum-PINN program is uninteresting.'' (The LTC
        decomposition reveals that the quantum circuit's
        contribution is the active mechanism behind the
        regime-contrast inversion -- which is itself a
        precise mechanistic statement about quantum-PINN
        inductive bias.)
\end{itemize}

The FALSIFIED verdict is a rigorous mechanistic null on a
specific hypothesis. It directly extends the
Bowles--Schuld~\cite{bowles2024better} methodological program:
when a quantum-ML advantage hypothesis is pre-registered, tested
with matched baselines and symmetric HPO and an LTC
decomposition, and the result is FALSIFIED, that result is the
scientific content. We treat it as such.
