% Section: Conclusions — P8 commit 9.

\section{Conclusions}
\label{sec:conclusions}

We pre-registered, executed, and aggregated a quantum
physics-informed neural network benchmark organized around the
Schuld--Fourier regime-dependent advantage
hypothesis~\cite{schuld2022right,schuld2021effect}. The benchmark
ran four quantum-PINN families on a hardness ladder of four
ODEs and four PDEs, three seeds each ($n = 24$ for the primary
solver verdict), with five matched classical baselines
(plain Neural-ODE, classical LTC, plain MLP, classical PINN,
known-structure skyline) and the complete 2$\times$2 fairness
matrix on the forecaster task (liquid$\times$quantum cross of
\texttt{LiquidQuantumCell}, \texttt{ClassicalLTCCell},
\texttt{NonLiquidQuantumCell}, and \texttt{PlainNeuralODECell}).

\textbf{The pre-registered $H_1$ regime-dependent quantum
advantage is FALSIFIED.} Across all eight non-fragile sensitivity
points (the only positive-CI verdict, P7.5 raw $n = 9$, is
sample-size-fragile and HPO-fragile and is superseded by every
subsequent row of Table~\ref{tab:master-verdicts}), the
paired-bootstrap 95\% confidence intervals on
$\dsmooth - \dbroad$ either include zero or exclude it in the
\emph{negative} direction. The primary solver verdict at
$n = 24$ has $\ddiff = -0.084$, CI $[-0.278, +0.061]$; the
primary forecaster verdict at $n = 9$ (with all five quantum
families including \texttt{rf\_qrc}) has $\ddiff = -0.501$,
CI $[-0.804, -0.244]$, statistically excluding zero in the
direction opposite the original prediction.

\textbf{The LTC decomposition mechanistically attributes the
inversion to the quantum circuit.} With all four corners of the
forecaster fairness 2$\times$2 filled, the quantum-isolated
$\ddiff = -0.616$ (CI $[-1.167, -0.178]$) is significantly
negative, while the liquid-isolated $\ddiff = +0.115$
(CI $[-0.097, +0.377]$) is the only verdict in the program
whose point estimate matches the original Schuld--Fourier
direction. The classical liquid-time-constant machinery alone
has the smooth-bin inductive bias the theory predicts; the
quantum circuit's contribution to the regime contrast destroys
it.

\textbf{Positive sub-findings remain.} The expanded matrix
surfaces two structural quantum advantages observable at zero
classical parameters in the quantum cell: \texttt{te\_qpinn\_qnn}
on \fhn{} (24$\times$ tighter seed variance and 2.5$\times$
lower mean error than the matched cPINN) and \texttt{rf\_qrc}
on the chaotic Lorenz cells (the strongest forecaster on
Lorenz s0 and s2). The H3 cross-tabulation identifies expressivity
(KL-to-Haar distance) as a candidate within-roster predictor of
per-cell $\Delta$ ($\rho = +0.518$, LOO-robust at $n = 9$);
significance at the program's sample size is insufficient, but
the trend's direction is consistent with the LTC decomposition's
mechanism attribution.

\textbf{The methodological contribution is the benchmark
framework itself.} The open-source pipeline at
\url{https://github.com/shawngibford/qlnn} implements the
Bowles--Schuld~\cite{bowles2024better} program in its
entirety: pre-registration with twelve openly-documented
amendments, paired-bootstrap inference, underfit and skyline
guards, symmetric HPO on three anchor cells, the all-to-all
contrast matrix in body-text tables, and the
\texttt{verify\_paper\_integrity.py} mechanical gate that
matches every cited number to a committed JSON file. The
P7.11 non-liquid quantum forecaster ablation completes the
fairness 2$\times$2 on the forecaster task -- to our knowledge
the first quantum-PINN benchmark to do so.

\textbf{Future work targets the mechanism.} The follow-up paper
applies three concrete interventions identified by the
mechanism analysis as plausibly relevant: Quantum Natural
Gradient optimization~\cite{stokes2020quantum} (targeting the
quantum-circuit training inefficiency the LTC decomposition
identifies), causal training weighting~\cite{wang2022causality}
(targeting the stiff-dynamics failure mode), and higher
data-reuploading depth at $L = 5$
(targeting the Fourier $K_{\max}$ ceiling identified in
Section~\ref{sec:mechanism-scalars}). The deferred Kuramoto
(12-dim) and KdV (third-order spatial) systems are also
queued for the follow-up; the mechanism gate for KdV's triple-
nested autodiff has been pre-cleared
(Section~\ref{sec:discussion-limitations}). Whether any of
these interventions recovers the $H_1$-predicted direction
remains an empirical question that the current benchmark cannot
answer; the methodological framework introduced here is what
makes the future answer falsifiable.
