% =====================================================================
% PRX Quantum submission: Regime-dependent quantum PINN benchmarking
% =====================================================================
% Compile: pdflatex main && bibtex main && pdflatex main && pdflatex main
% Or run: bash paper/build.sh
%
% Build status (P8 commit 1): SCAFFOLD ONLY. Title + abstract +
% section stubs. Numerical claims are added section-by-section in
% subsequent commits, with each cited number traced to a
% `results/` file via `scripts/verify_paper_integrity.py`.
% =====================================================================
\documentclass[%
  prx,
  twocolumn,
  amsmath,
  amssymb,
  aps,
  reprint,
  superscriptaddress,
  floatfix,
]{revtex4-2}

% Packages
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{hyperref}
\usepackage{xcolor}
\hypersetup{colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue}
\usepackage{siunitx}
\usepackage{microtype}

% Custom commands for our framework
\newcommand{\relltwo}{\mathrm{relL}^2}
\newcommand{\nsmooth}{n_{\mathrm{smooth}}}
\newcommand{\nbroad}{n_{\mathrm{broad}}}
\newcommand{\dsmooth}{\Delta_{\mathrm{smooth}}}
\newcommand{\dbroad}{\Delta_{\mathrm{broad}}}
\newcommand{\ddiff}{\Delta_{\mathrm{diff}}}
\newcommand{\qlnn}{QLNN}
\newcommand{\cpinn}{cPINN}

% Common abbreviations for system names
\newcommand{\fhn}{FitzHugh--Nagumo}
\newcommand{\lv}{Lotka--Volterra}
\newcommand{\vdp}{Van der Pol}
\newcommand{\ac}{Allen--Cahn}

\begin{document}

% Global glue-stretch budget. Two-column revtex with long ansatz
% names + nested math labels routinely produces 1-95pt overfull
% boxes that look fine in print but trigger noisy log warnings.
% Slightly looser inter-word stretch eliminates the cosmetic
% violations without affecting readability.
\sloppy
\emergencystretch=3em

% =====================================================================
% Title, authors, abstract
% =====================================================================
\title{%
  Regime-dependent advantage in quantum physics-informed neural
  networks: a pre-registered comparison on an ODE/PDE hardness
  ladder%
}

\author{Shawn Gibford}
\email{gibfords@gmail.com}
\affiliation{Independent}

\date{\today}

\begin{abstract}
We pre-register and execute a head-to-head benchmark of four quantum
physics-informed neural network (PINN) families against
capacity-matched classical PINN and Neural-ODE baselines, on a
hardness ladder of four ordinary and four partial differential
equations at three random seeds each. Following the methodology
proposed by Bowles, Ahmed, and Schuld for credible quantum
machine-learning benchmarks \textemdash{} matched training budgets,
paired-bootstrap confidence intervals, an underfit guard, and a
known-structure skyline \textemdash{} we test the pre-registered
hypothesis that quantum PINNs hold a regime-dependent advantage
favoring smooth/periodic over broadband/multiscale dynamics. The
hypothesis is FALSIFIED. Across both PRIMARY verdicts \textemdash{} the
full-ladder solver task at $n=24$ and the forecaster task at $n=9$
\textemdash{} the regime-dependent advantage is statistically
indistinguishable from zero, and the point estimate trends, if
anything, in the opposite (broadband-favoring) direction. One positive
sub-finding survives the falsification: the trainable-embedding quantum
PINN with a QNN encoder achieves markedly tighter seed-to-seed variance
and lower mean error than the matched classical PINN on stiff
fast--slow (\fhn{}) dynamics. We release the full open-source benchmark
framework, with every cited number mechanically verified against a
committed results file.
\end{abstract}

\maketitle

% =====================================================================
% Body sections — modular includes, one .tex per section
% =====================================================================
\input{sections/01_introduction}
\input{sections/02_methods}
\input{sections/03_solver_results}
\input{sections/04_forecaster_results}
\input{sections/05_h1_verdict}
\input{sections/06_mechanism}
\input{sections/07_discussion}
\input{sections/08_conclusions}

% =====================================================================
% Acknowledgments
% =====================================================================
\begin{acknowledgments}
This work was carried out as an independent research project. The
author thanks the open-source PennyLane, JAX, Equinox, Diffrax, and
optax communities for the core scientific computing infrastructure
that made this benchmark possible. Anthropic's Claude provided
research assistance throughout. The author declares no competing
interests.
\end{acknowledgments}

% =====================================================================
% Bibliography
% =====================================================================
\bibliographystyle{apsrev4-2}
\bibliography{references}

\end{document}
